Model-based variable selection for regression with highly correlated variables.

### 2014-05-20 www/article13.tex
up miss
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@614 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

@@

>>>>

\clearpage

@@

\begin{figure}[h!]
	\begin{minipage}[l]{.48\linewidth}
			\includegraphics[height=180px,width=245px]{figures/res_article/bon_gauche.png} 
			\caption{Number of $\boldsymbol{X_r}$ covariates found with both $BIC$ (dotted) and $BIC_+$ (plain)}
	\end{minipage} \
   \begin{minipage}[r]{.48\linewidth}
			\includegraphics[height=180px,width=240px]{figures/res_article/faux_gauche.png} 
			\caption{Number of covariates wrongly set in $\boldsymbol{X}_r$ with both $BIC$ (dotted) and $BIC_+$ (plain)} 
   \end{minipage}
\end{figure}
